ZCB Pricing

### 2018-07-24 ZCB Pricing .Rmd
Changes to monte carlo

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[j-1] # Euler Discretization
      dr_i= alpha*(beta-sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[j-1]
      sim_path[j,i]=sim_path[j-1,i]+dr
      sim_path_inv[j,i]=sim_path_inv[j-1,i]+dr_i

@@

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[j-1]# Euler Discretization
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }

>>>>

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i] # Euler Discretization
      dr_i= alpha*(beta-sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i]
      sim_path[j,i]=sim_path[j-1,i]+dr
      sim_path_inv[j,i]=sim_path_inv[j-1,i]+dr_i

@@

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[i]# Euler Discretization
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }
